\documentclass[12pt]{article}
\usepackage[a4paper,margin=1cm,footskip=.5cm]{geometry}
\usepackage[]{authblk}
\usepackage{graphicx}
\usepackage{hanging}
\usepackage{indentfirst}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{color}
\usepackage{lipsum}
\usepackage[breaklinks]{hyperref}
\usepackage[all]{hypcap}
\definecolor{darkblue}{rgb}{0.0,0.0,0.5}
%\onehalfspace
\setlength{\evensidemargin}{0in}
\setlength{\oddsidemargin}{0in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.75in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9in} % This changed from 9in
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{0.15in}
\setlength{\topskip}{0mm}
\setlength{\voffset}{-0.5in}
\setlength{\parindent}{1cm}
%\setlength{\headheight}{99pt}
\setlength{\headheight}{0.5in}
\parskip = 1mm
\pagestyle{plain}

\definecolor{citescol}{RGB}{73,0,165}
\definecolor{urlscol}{RGB}{3,0,255}
\definecolor{linkscol}{RGB}{187,24,0}
\definecolor{isured}{RGB}{204,0,51}
\definecolor{isukhaki}{RGB}{76,69,43}
\definecolor{coolblack}{rgb}{0.0, 0.18, 0.39}
\let\oldtextbf\textbf
\renewcommand{\textbf}[1]{\textcolor{coolblack}{\oldtextbf{#1}}}

\hypersetup{colorlinks=true,linkcolor=linkscol,citecolor=citescol,urlcolor=urlscol}

\begin{document}

\thispagestyle{fancy}
\begin{flushright}
\today
\end{flushright}
\vspace{2mm}
\begin{flushleft}
\textbf{Course Title:} Genomics and Transcriptomics \\
\textbf{Course Number:} GBIO 493 (undergraduate)/ GBIO 593 (graduate)\\
\textbf{Course Website:}  \url{https://paleantology.github.io/SELUGandT/} \\

\textbf{Course Date:} Spring 2018 \\

\textbf{Course Meeting Times:} Tuesday and Monday 1PM - 3:50 PM \\
\textbf{Course Meeting Location:} Biology Building 210 \\
\end{flushleft}

\bigskip

\begin{flushleft}
\textbf{Course Faculty:} Dr. April Wright \& Dr. Raul Diaz \\
\textbf{Office:} Biology Building 403 (April) \&  332 (Raul)\\
\textbf{Office Phone:} 5556 (April) \& 5295 (Raul) \\
\textbf{Email:} april.wright@selu.edu \& raul.diaz@selu.edu  \\
\textbf{Office Hours:} April: Monday, Tuesday, Thursday, Friday 10-12am. Raul: Monday & Wednesday 1-3pm. And by appointment \\

\end{flushleft}

\bigskip

\begin{flushleft}

\textbf{Course Description}
This is a 3-unit course. In this course, we will explore the fundamentals of genomics and transcriptomics. Using hands-on laboratory and computational methods, you will become familiar with the types of cutting-edge analyses that researchers in this discipline use in pursuit of questions about biology.

\end{flushleft}

\bigskip
\begin{flushleft}

\textbf{Course Objectives}

\begin{itemize}

\item Understand why researchers sequence genomes and transcriptomes in biology.
\item Explain how experimental design relates to the biological questions being asked.
\item Use the command line to explore and process biological data
\item Describe workflows and software that are appropriate for different genomic and transcriptomic applications.

\end{itemize}
\end{flushleft}

\bigskip

\begin{flushleft}
\textbf{Assessment}
A grade of `C" or better in this course is required to satisfy the curriculum requirements for the College of Science and Technology. There are a total of 500 points in this course. They are distributed as follows:

\begin{itemize}
\item Standard Exams
\item \textbf{Project One:} 100 pts
\item \textbf{Homeworks:} 100 pts
\item \item \textbf{Quizzes:} 100 pts
\item \textbf{Project two:} 100 pts
\item \textbf{Group presentation:} 100 pts
\end{itemize}	

\bigskip

\textbf{Grades will be assigned as follows:}

A: 450-500 points, B: 400-449 pts, C: 350-399 pts
\end{flushleft}

\bigskip

\begin{flushleft}
\textbf{Attendance and Make-Up}
\end{flushleft}

 Attendance is expected. Homeworks will be posted via the course websited, and turned in via GitHub. Homework will be due every Friday on non-exam weeks. Because they will be available for the entire week before they are due, \textbf{no make ups} will be available for assignments unless prior approval is granted. Quizzes will be Tuesday at the start of class. \par
 If you are aware in advance of absences, please let us know. The more information we have, the easier it is for us to accommodate you. \par

\begin{flushleft}
\textbf{Important Dates}
\end{flushleft}

\begin{itemize}
\item Feb. 8: Academic Checkpoint 1	
\item March 9: Academic Checkpoint 2	
\item March 23, 12:30: Last drop period
\item May 4: Last day of classes

\end{itemize}


\end{document}
